\textsc{PAPERCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-03-27 paper/colm_submission/colm2024_conference.tex
Tweaking COLM

   The concept of learning task-agnostic representations via self-supervised and contrastive learning has been applied within astrophysics \citep{slijepcevic2024radio,stein2021self,hayat2021self,slijepcevic2022learning} and used for downstream tasks like object similarity search \citep{stein2021self}, gravitational lens finding \citep{stein2022mining}, estimation of Galactic distances \citep{hayat2021estimating}, identification of rare galaxies \citep{walmsley2023rare}, and data compression \citep{akhmetzhanova2024data}. For a recent review of contrastive learning in astrophysics, see \citet{huertas2023brief}. 
   %
   Beyond applications to a single modality, \textsc{AstroCLIP}~\citep{lanusse2023astroclip} recently used contrastive learning to learn a joint representation between galaxy images and associated spectra, showing that the learned representation embodies relevant physical properties and can be effectively used for downstream tasks like redshift and mass estimation.
   %
   \citet{bowles2023radio,bowles2022new} introduced a method to associate radio galaxy images with a natural language description of their morphology by using human-generated descriptions, with the goal of deriving semantic morphology classes and using them for classification.
  %  %
  In contrast with previous work, our application is the first to associate astronomical observation with the text modality in a generalist framework, showcasing the potential of language models in specialized scientific domains like astronomy.
  %

@@

  The following curated categories are used in the text retrieval experiment in Sec.~\ref{sec:results}.
%
These are derived by initially prompting \textsc{Claude 2}\footnote{\url{https://claude.ai/}}, having attached a subsample of 30 proposal abstracts in the online interface to be used as context, to produce a list of categories corresponding to typical HST observations. The list is then manually curated to remove similar entries and ensure a representative sample of categories. \\

>>>>

   The concept of learning task-agnostic representations via self-supervised and contrastive learning has been applied within astrophysics \citep{slijepcevic2024radio,stein2021self,hayat2021self,slijepcevic2022learning} and used for downstream tasks like object similarity search \citep{stein2021self}, gravitational lens finding \citep{stein2022mining}, estimation of Galactic distances \citep{hayat2021estimating}, identification of rare galaxies \citep{walmsley2023rare}, and data compression \citep{akhmetzhanova2024data}. For a recent review of contrastive learning in astrophysics, see \citet{huertas2023brief}. 
   %
   Beyond applications to a single modality, \textsc{AstroCLIP}~\citep{lanusse2023astroclip} recently used contrastive learning to learn a joint representation between galaxy images and associated spectra, showing that the learned representation embodies relevant physical properties and can be effectively used for downstream tasks like redshift and mass estimation.
   %
   \citet{bowles2023radio,bowles2022new} introduced a method to associate radio galaxy images with a natural language description of their morphology by using human-generated descriptions, with the goal of deriving semantic morphology classes and using them for classification.
  %  %
  In contrast with previous work, our application is the first to associate astronomical observation with the text modality in a task-agnostic manner, showcasing the potential of language models in specialized scientific domains like astronomy.
  %

@@

  The following curated categories are used in the text retrieval experiment in Sec.~\ref{sec:results}.
%
These are derived by initially prompting \textsc{Claude 2}\footnote{\url{https://claude.ai/}}, having attached a subsample of 30 proposal abstracts in the online interface to be used as context, to produce a list of categories corresponding to typical HST observations. The list is then manually curated to remove similar entries and ensure a representative sample of categories. \\ \\
